Finite-state morphological transducers for three Kypchak languages

### 2014-03-22 kipchak-lrec-2013/kipchak-paper.tex
improve placement of graph
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@51077 72bbbca6-d526-0410-a7d9-f06f51895060
add numbers of kumyk
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@51095 72bbbca6-d526-0410-a7d9-f06f51895060
smallcaps
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@51096 72bbbca6-d526-0410-a7d9-f06f51895060

\begin{figure}
%\centering
\hspace{-15pt}
    \rotatebox{-90}{
\includegraphics[width=0.4\textwidth]{graphs/kumyk-yoldash-coverage}
}

@@

In Kazakh, ‹е› is a front diphthong (e.g., ‹елдің› `country-\tags{gen}'), but in e.g., family names with Russian morphology, it harmonises as a back vowel (e.g., ‹Назарбаевтың› `Nazarbayev-\tags{gen}').

@@

\begin{table}
\begin{center}
	\begin{tabular}{lrr}
	\toprule
		\textbf{Language} & \textbf{Precision (\%)} & \textbf{Recall (\%)} \\
	\midrule
		Kazakh & 98.61 &  57.98 \\
		Tatar & 95.03 & 85.65 \\
		Kumyk & - & - \\
	\bottomrule
	\end{tabular}
	\caption{Precision and recall presented as percentages}
	\label{table:precrecall}
\end{center}
\end{table}

>>>>

\begin{figure}
%\centering
\hspace{-35pt}
    \rotatebox{-90}{
\includegraphics[width=0.38\textwidth]{graphs/kumyk-yoldash-coverage}
}
~\\
~\\

@@

In Kazakh, ‹е› is a front diphthong (e.g., ‹елдің› `country-\tags{gen}'), but in e.g., family names with Russian morphology, it harmonises as a back vowel (e.g., ‹Назарбаевтың› `Nazarbayev-{\sc gen}').

@@

\begin{table}
\begin{center}
	\begin{tabular}{lrr}
	\toprule
		\textbf{Language} & \textbf{Precision (\%)} & \textbf{Recall (\%)} \\
	\midrule
		Kazakh & 98.61 &  57.98 \\
		Tatar & 95.03 & 85.65 \\
		Kumyk & 96.57 & 69.11 \\
	\bottomrule
	\end{tabular}
	\caption{Precision and recall presented as percentages}
	\label{table:precrecall}
\end{center}
\end{table}
